### 2020-06-04 writeup/experiments.tex
wip

We connect our theory to pratical problems of interest.
First, we validate the single-task based metric on text and image classification tasks.
We show that for both datasets, single-task learning results can help predict positive or negative transfer in multi-task learning.
Second, we show that our proposed incremental training schedule improves the training efficiency of multi-task learning for predicting a particular target task.
%Third, we measure the data efficiency ratio of multi-task learning on six sentiment analysis tasks.
Finally, we validate the three components of our theory and measure the data efficiency of multi-task learning on text classification tasks.

>>>>

We connect our theory to pratical problems of interest.
(i) We validate the single-task based metric on text and image classification tasks.
We show that for both datasets, single-task learning results can help predict positive or negative transfer in multi-task learning.
(ii) We show that our proposed incremental training schedule improves the training efficiency of multi-task learning for predicting a particular target task.
%Third, we measure the data efficiency ratio of multi-task learning on six sentiment analysis tasks.
(iii) We validate our theoretical results in Section \ref{sec_insight} on text classification tasks.
